The Morality of Arbitrage

### 2017-04-22 Draft/draft.Rmd
Adding thoughts and renderer script.

@@

>>>>

> [T]he shipper who earns his living from using otherwise empty or half-filled journeys of tramp-steamers, or the estate
> agent whose whole knowledge is almost exclusively one of temporary opportunities, or the *arbitrageur* who gains from
> local differences of commodity prices, are all performing eminently useful functions based on special knowledge of
> circumstances of the fleeting moment not known to others.
	-- F.A. Hayek

@@

# Dutch Books

#

### 2017-04-22 Draft/draft.tex
Adding thoughts and renderer script.

@@

>>>>

\begin{quote}
{[}T{]}he shipper who earns his living from using otherwise empty or
half-filled journeys of tramp-steamers, or the estate agent whose whole
knowledge is almost exclusively one of temporary opportunities, or the
\emph{arbitrageur} who gains from local differences of commodity prices,
are all performing eminently useful functions based on special knowledge
of circumstances of the fleeting moment not known to others. -- F.A.
Hayek
\end{quote}

@@

\section{Dutch Books}\label{dutch-books}

\section{}\label{section}
